Array Programming with NumPy

### 2020-08-12 methods.tex
Remove fig reference
Rearrange methods
Typo
More typos

@@

The \emph{universal functions}, or more concisely, \emph{ufuncs},
are functions written in C that implement efficient looping over
NumPy arrays. An important feature of ufuncs is the built-in
implementation of \emph{broadcasting}.  For example, the function
\texttt{arctan2(x, y)} is a ufunc that accepts two values and computes
$\tan^{-1}(y/x)$.  When arrays are passed in as the arguments,
the ufunc will take care of looping over the dimensions of the inputs
in such a way that if, say, \texttt{x} is a 1-D array with length 3, and
\texttt{y} is a 2-D array with shape $2 \times 1$, the output will be
an array with shape $2 \times 3$ (Fig.~\ref{fig:array-concepts}c).
The ufunc machinery takes care
of calling the function with all the appropriate combinations of
input array elements to complete the output array.
The elementary arithmetic operations of addition, multiplication, etc.,
are implemented as ufuncs, so that broadcasting also applies to expressions
such as \texttt{x + y * z}.

\subsection*{Computing libraries.}

@@

The NumPy module mainly provides interfaces to established
implementations of the LAPACK (Linear Algebra PACKage) \cite{LAPACK}
interface.  LAPACK itself, which was first released in 1992, is, in
turn, based on the EISPACK and LINPACK open-source libraries. It is
part of Netlib, a repository of mathematical software, papers, and
databases, that has a long history of open, community-wide
development \cite{dongarra1990lapack,dongarra2008netlib}. For improved
performance, NumPy links to an accelerated BLAS (Basic Linear Algebra
Subprograms) implementation, most commonly OpenBLAS
(http://www.openblas.net/).

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{scripts/PRs-using-CURRENT_MAINTAINERS.pdf}
    \caption{\textbf{Number of pull requests merged into the NumPy master branch for each
        quarter since 2012.} The total number of PRs is indicated with the
        lower blue area showing the portion contributed by current or previous
        maintainers.}\label{fig:prs-over-time}
\end{figure}

@@

\section*{Conclusion}

>>>>

\section*{History}

\section*{Version control and collaboration}

@@

The \emph{universal functions}, or more concisely, \emph{ufuncs},
are functions written in C that implement efficient looping over
NumPy arrays. An important feature of ufuncs is the built-in
implementation of \emph{broadcasting}.  For example, the function
\texttt{arctan2(x, y)} is a ufunc that accepts two values and computes
$\tan^{-1}(y/x)$.  When arrays are passed in as the arguments,
the ufunc will take care of looping over the dimensions of the inputs
in such a way that if, say, \texttt{x} is a 1-D array with length 3, and
\texttt{y} is a 2-D array with shape $2 \times 1$, the output will be
an array with shape $2 \times 3$.
The ufunc machinery takes care
of calling the function with all the appropriate combinations of
input array elements to complete the output array.
The elementary arithmetic operations of addition, multiplication, etc.,
are implemented as ufuncs, so that broadcasting also applies to expressions
such as \texttt{x + y * z}.

\subsection*{Computing libraries}

@@

The NumPy module mainly provides interfaces to established
implementations of the LAPACK (Linear Algebra PACKage) \cite{LAPACK}
interface.  LAPACK itself, which was first released in 1992, is, in
turn, based on the EISPACK and LINPACK open-source libraries. It is
part of Netlib, a repository of mathematical software, papers, and
databases, that has a long history of open, community-wide
development \cite{dongarra1990lapack,dongarra2008netlib}. For improved
performance, NumPy links to an accelerated BLAS (Basic Linear Algebra
Subprograms) implementation, most commonly OpenBLAS
(\url{http://www.openblas.net/}).

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{scripts/PRs-using-CURRENT_MAINTAINERS.pdf}
    \caption{\textbf{Number of pull requests merged into the NumPy master branch for each
        quarter since 2012.} The total number of PRs is indicated, with the
        lower blue area showing the portion contributed by current or previous
        maintainers.}\label{fig:prs-over-time}
\end{figure}

@@
